# Analysis

```{r, message=FALSE}
library(lavaan)
library(tidyverse)
library(here)
library(ggplot2)
library(scales)
library(showtext)
library(ggstance)
library(extrafont)
library(kableExtra)
```

Set figure options like before.
```{r}
# Plotting options
Font <- "Titillium Web"
font_add_google(Font, Font)
theme_set(
  theme_linedraw(
    base_family = Font,
    base_size = 12
  ) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank()
    )
)

col1 <- "#2980b9"
col2 <- "#2980b9"
```

Load the cleaned data set from the previous section.
```{r}
data_path <- here("data", "cleaned_data.rds")
if (file.exists(data_path)) {
  d <- read_rds(file = data_path)
} else {
  stop(str_glue("{data_path} doesn't exist, run `01-process.Rmd` to create it."))
}
```

## Run model

The syntax for lavaan.
Note that we constrain the cross-lagged effects to be the same, but within each game (so the effects can be different for the games).
See explanation here: <https://lavaan.ugent.be/tutorial/groups.html>
```{r}
riclpm_constrained <- "
  # Create between components (random intercepts)
  RIx =~ 1*x1 + 1*x2 + 1*x3
  RIy =~ 1*y1 + 1*y2 + 1*y3

  # Create within-person centered variables
  wx1 =~ 1*x1
  wx2 =~ 1*x2
  wx3 =~ 1*x3
  wy1 =~ 1*y1
  wy2 =~ 1*y2
  wy3 =~ 1*y3

  # Estimate the lagged effects between the within-person centered variables (constrained).
  wx2 ~ c(bxa, bxo)*wx1 + c(gxa, gxo)*wy1
  wy2 ~ c(gya, gyo)*wx1 + c(bya, byo)*wy1
  wx3 ~ c(bxa, bxo)*wx2 + c(gxa, gxo)*wy2
  wy3 ~ c(gya, gyo)*wx2 + c(bya, byo)*wy2

  # Estimate the covariance between the within-person centered
  # variables at the first wave.
  wx1 ~~ wy1 # Covariance

  # Estimate the covariances between the residuals of the
  # within-person centered variables (the innovations).
  wx2 ~~ wy2
  wx3 ~~ wy3

  # Estimate the variance and covariance of the random intercepts.
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2
  wx3 ~~ wx3
  wy3 ~~ wy3
"
```

Transform the data to wide format for lavaan to take the arguments above.
```{r}
d_riclpm <- d %>%
  select(
    Game, pid, wid,
    Hours, Angry
  ) %>%
  # Long format on anger (outcome)
  pivot_longer(
    Angry,
    names_to = "y_var", values_to = "y"
  ) %>%
  # Long format on hours (predictor)
  pivot_longer(
    Hours,
    names_to = "x_var", values_to = "x"
  ) %>% 
  pivot_wider(
    names_from = wid,
    values_from = c(x,y),
    names_sep = ""
  )
```

Fitting the model.
```{r}
lavaan_fit <- lavaan(
  riclpm_constrained,
  data = d_riclpm,
  missing = "ml",
  meanstructure = TRUE,
  int.ov.free = TRUE,
  group = "Game"
)
```

Inspecting summary.
```{r}
summary(lavaan_fit)
```

Get parameter estimates for plot.
Note: The standardized estimates aren't the same across waves because we didn't put equality constraints on the variances -- only the unstandardized ones are identical.
```{r}
params <- 
  bind_rows(
    parameterestimates(lavaan_fit) %>% 
      mutate(Type = "Unstandardized"),
    standardizedsolution(lavaan_fit) %>%
      rename(est = est.std) %>% 
      mutate(Type = "Standardized")
  ) %>% 
  as_tibble() %>% 
  rename(Game = group) %>% 
  mutate(
    Game = factor(if_else(Game == 1, "Apex Legends", "Outriders"))
  ) %>% 
  mutate(
    label = if_else(lhs == "RIx" & rhs == "RIy", "Covariance", label)
  ) %>% 
  mutate(
    Outcome = case_when(
      str_starts(lhs, "wx") ~ "Hours",
      str_starts(lhs, "wy") ~ "Angry",
      TRUE ~ NA_character_
    ),
    Predictor = case_when(
      str_starts(rhs, "wx") ~ "Hours",
      str_starts(rhs, "wy") ~ "Angry",
      TRUE ~ NA_character_
    )
  ) %>%
  mutate(
    `Parameter type` = case_when(
      lhs == "RIx" & rhs == "RIy" ~ "Covariance",
      Predictor == Outcome ~ "Autoregression",
      Predictor != Outcome ~ "Cross-lagged",
      TRUE ~ NA_character_
    )
  ) %>%
  mutate(
    Direction = case_when(
      `Parameter type` == "Cross-lagged" ~ str_glue('{Predictor}[plain("[t-1]")]%->%{Outcome}[plain("[t]")]'),
      TRUE ~ NA_character_
    ),
    Direction = as.factor(Direction)
  ) %>% 
  filter(!label == "") %>% 
  mutate(
    across(
      c(est, ci.lower, ci.upper),
      ~ round(.x, digits = 2)
    )
  ) %>%
  select(
    Predictor,
    Outcome,
    `Parameter type`,
    Direction,
    Type,
    Game,
    Estimate = est,
    `Lower CI` = ci.lower,
    `Upper CI` = ci.upper
  ) %>%
  distinct() %>% 
  mutate(
    across(
      c(Predictor, Outcome, Direction),
      ~ as.factor(str_replace(.x, "Angry", "`Aggressive affect`")) # for labelling figure
    )
  )

params %>% 
  select(-Direction) %>% 
  mutate( # temporarily remove backticks (purely cosmetic, for table below)
    across(
      c(Predictor, Outcome),
      ~ str_replace(.x, "`Aggressive affect`", "Aggressive affect") # for labelling figure
    )
  ) %>% 
  kbl(caption = "Parameter from RICLPM") %>% 
  kable_styling(full_width = FALSE, font_size = 12) 
  
```
## Figure 4

Then a forest plot of the unstandardized cross-lagged effects.
```{r, message=FALSE}
text_estimates <- 
  params %>% 
  filter(Type == "Unstandardized", `Parameter type` == "Cross-lagged") %>% 
  mutate(
    label = str_glue("{Estimate} [{`Lower CI`}, {`Upper CI`}]"),
    x = rep(0.25, 4),
    y = c(rep(2.1, 2), rep(1.1, 2))
  )

params %>%
  filter(Type == "Unstandardized", `Parameter type` == "Cross-lagged") %>% 
  mutate(
    Direction = fct_rev(Direction), # not in alphabetical order
    Game = fct_rev(Game),
    estimate_text = str_glue("{Estimate} [{`Lower CI`}, {`Upper CI`}]")
  ) %>% 
  ggplot(aes(Estimate, Game)) +
  geom_vline(xintercept = 0, lty = 2, size = .25) +
  geom_pointrange(
    aes(xmin = `Lower CI`, xmax = `Upper CI`),
    size = 0.8
  ) +
    scale_x_continuous(
    breaks = pretty_breaks()
  ) +
  xlab("Estimated cross-lagged effect [95%CI]") +
  xlim(-0.4, 0.4) +
  facet_wrap(
    ~ Direction,
    labeller = labeller(.rows = label_parsed)
  ) +
  geom_text(
    data = text_estimates,
    mapping = aes(x = x, y = y, label = label)
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank(),
    panel.grid.major.y = element_line(color = "lightgrey"),
    
  )
```

